Online Multiclass Linear Classification with Bandit Feedback

### 2019-01-16 arxiv-version/np-hardness-of-the-weak-labeling-problem.tex
some minor modification to arxiv version (np-hard section)

The hardness proof is based on a reduction from the set splitting problem, which is proven to be NP-complete by Lovasz \chenyu{Reference needed}, to our weak labeling problem. The reduction is adapted from Avrim Blum \chenyu{Reference needed}. 
\begin{figure}[h]
\begin{framed}
\begin{center}
    \textbf{Set Splitting}
\end{center}
\textbf{Given: } A finite set $S$ and a collection $C$ of subsets $c_i$ of $S$. \\
\textbf{Question: } Do there exist disjoint sets $S_1$ and $S_2$ such that $S_1 \cup S_2 = S$ and $\forall i, c_i\not\subseteq S_1$ or $c_i\not\subseteq S_2$? 
\end{framed}
\end{figure}

>>>>

The hardness proof is based on a reduction from the set splitting problem, which is proven to be NP-complete by Lovasz \cite{garey1979computers}, to our weak labeling problem. The reduction is adapted from \cite{blum1989training}. 
\begin{figure}[h]
\begin{framed}
\begin{center}
    \textbf{Set Splitting}
\end{center}
\textbf{Given: } A finite set $S$ and a collection $C$ of subsets $c_i$ of $S$. \\
\textbf{Question: } Do there exist disjoint sets $S_1$ and $S_2$ such that $S_1 \cup S_2 = S$ and $\forall i, c_i\not\subseteq S_1$ or $c_i\not\subseteq S_2$? 
\end{framed}
\end{figure}
